
\documentclass[10pt]{res}  
\usepackage{hyperref}
\usepackage{helvet}   
\usepackage[nodate]{datetime}
\usepackage{makeidx}

\newsectionwidth{0pt} % Stops section indenting
\date{\displaydate{date}}
\usepackage{multicol}
\usepackage{graphicx} %package to manage images
\graphicspath{ {images/} }
\usepackage{amsmath}
 


\begin{document} 



  
{\huge Curriculum Vitae of } 
{\huge Md. Rasheduzzaman} \\
 Software Project Manager, \\
 Department of Software Application Development,\\
 SOOKH, Dhaka, Bangladesh.\\
 Email:  \href{mailto:jmrashed@gmail.com}{jmrashed@gmail.com} \\
 Mobile:  +8801910077628 \\
\href{https://www.linkedin.com/in/jmrashed}{https://www.linkedin.com/in/jmrashed} \\

 

\begin{resume}

 

\section{OBJECTIVE}

\vspace{7pt}  
My career objective is to utilize my 6+ years of experience as a Tech Lead officer and project management expertise to drive the success and growth of the company. I aim to ensure timely accomplishment of all identified goals and schedules to contribute significantly to the company's long-term success.


\section{SKILLS SUMMARY}

\vspace{7pt}  
My expertise in project management, project life cycle, and leadership includes requirements analysis, costing, budgeting, scheduling, effective communication, testing, quality assurance, and support. Due to my exceptional abilities in team mentoring, building, and supervision, as well as managing client relationships and vendors, I am confident that I can be of value to any company.

\vspace{7pt} 


 
\section{PROFESSIONAL EXPERIENCES [ 5 YEARS]} 
 
\vspace{20pt}
\textbf{Tech Lead Officer ( June 2022 to till now)}\\
Onest Tech Ltd, Banani, Dhaka-1212, Bangladesh\\
\vspace{6px}  
\textbf{Duty \& Responsibilities:}
    \begin{itemize}
        \item Managing a team of software developers and IT professionals to ensure that all projects are completed efficiently, effectively, and on-time.
        \item Developing and implementing software solutions that meet or exceed stakeholder expectations.
        \item Collaborating with cross-functional teams to identify technical requirements, analyze data, and implement solutions that optimize business processes.
        \item Providing technical leadership to the team, coaching and mentoring team members, and ensuring that they have the resources and support they need to succeed.
        \item Developing and implementing best practices, standards, and policies to ensure that all software development projects are of the highest quality.
        \item Staying up-to-date with industry trends, new technologies, and emerging best practices to inform strategic decision-making and ensure that the team remains competitive in the marketplace.
    \end{itemize}  

  
\vspace{20pt}
\textbf{Project Manager ( February 2021 to May 2022)}\\
Onest Tech Ltd, Banani, Dhaka-1212, Bangladesh\\
\vspace{6px}  
\textbf{Duty \& Responsibilities:}
    \begin{itemize}
        \item Planning and executing all phases of the project life-cycle, from inception to completion, including scope management, requirements management, schedule and timeline management, and risk management.
        \item Ensuring that all projects are completed on-time, within scope, and within budget while maintaining the highest level of quality standards.
        \item Ensuring effective communication and collaboration among project team members and stakeholders.
        \item Maintaining project documentation, including project plans, status reports, and meeting minutes.
        \item Ensuring compliance with organizational policies and procedures, as well as relevant laws and regulations.
    \end{itemize} 


 
\vspace{20pt}
\section{Software Team Lead  (Remotely for Covid 19) ( January 2020 to January 2021) - 1 Year}
 Department of Web Development, AL Haramain Perfuimes LLC.\\
\textbf{Duty \& Responsibilities:}
\begin{itemize}
\item Managing people:
    \begin{itemize} 
        \item Acts as a project leader
        \item Communication with stakeholders/Investor/Clients 
        \item Strong team-building
    \end{itemize} 
\item Managing project:
    \begin{itemize} 
        \item Monitors progress and performance
        \item Risk analysis at every phase 
    \end{itemize}
    
    \item Successful Completion
        \begin{itemize} 
            \item Developing and directing software system validation and testing methods
            \item Working closely with clients and cross-functional departments to communicate project statuses and proposals
            \item Testing new software and fixing bugs.
        \end{itemize}
\end{itemize}
 
  

 
\vspace{20pt}
\section{Project Manager (July 2018 to 31 December 2020) - 2+ Years}
 Department of Software Development, Spondon IT Limited, Bangladesh.\\
\textbf{Duty \& Responsibilities:}
\begin{itemize}
    \item Activity and resource planning 
    \item Organizing and motivating a project team 
    \item Cost estimating and developing the budget 
    \item Ensuring customer satisfaction 
    \item Analyzing and managing project risk 
    \item Monitoring progress 
    \item Managing reports and necessary documentation 
\end{itemize}

 
 

 
\vspace{20pt}
\section{Senior Software Engineer (January 2017 to June 2018) - 1.5 Years}
 Department of Broadcast engineering, Boishakhi Media Limited, Bangladesh\\
\textbf{Duty \& Responsibilities:}
    \begin{itemize}
        \item Design, develop, and implement applications that support day-to-day operations.
        \item Plan, develop, and implement large-scale projects from conception to completion.
        \item Develop and architect life-cycle of projects working on different technologies and platforms.
        \item Interface with clients and gather business requirements and objectives.
        \item Design, develop, and implement new integration.
        \item Execute system development and maintenance activities.
        \item Source Control: Git, Mercurial, SVN, etc
    \end{itemize}




 
\vspace{20pt}
\section{Software Engineer (January 2016 to December 2016) - 1 Year}
 Department of IT, United Group Limited, Bangladesh\\
\textbf{Duty \& Responsibilities:}
    \begin{itemize}
        \item Execute full software development life cycle (SDLC) 
        \item Write well-designed, testable code 
        \item Integrate software components into a fully functional software system
        \item Document and maintain software functionality
        \item Troubleshoot, debug and upgrade existing systems   
        \item Website and software application designing, building, or maintaining.
        \item Editing, writing, or designing Website content, and directing team members who produce content.
        \item Software documentation \& Problem solving and Teamwork 
    \end{itemize}
 


 
\vspace{20pt}
\section{Technical Skill} 
\begin{itemize}
        \item \textbf{Technical Writing and Tools:} Yed, Latex, Latexdraw, etc.
        \item \textbf{Programming and Databases:} C/C++, SQL, PHP, MongoDB, GraphQL, HTML, CSS, JavaScript, jQuery, Ajax, NodeJs, WordPress etc.
        \item \textbf{Project Management Skills:} Planning, Risk management, Budgeting, Tracking and monitoring, Time management, Problem solving, Adaptability etc.
        \item \textbf{Software Engineering Skills:} Coding and Computer Programming, Software Testing, Object-Oriented Design (OOD), Software Development etc.
        \item \textbf{SEO Tools:}  (Google Insights, Keywordtool.io, Google Analytic, Google Trends, Keyword Shitter)
        \item \textbf{Device Integration with system:} P5100 Fingerprint Device, Mini A8 GPS Tracker, ZKTeco Fingerprint

\end{itemize}


 
 
\vspace{20pt}  
\section{\centerline{EDUCATIONAL QUALIFICATIONS}} 
 
\vspace{10pt}  

\textbf{B.Sc. in Computer Science and Engineering (CSE) } \\ 
\href{http://www.stamforduniversity.edu.bd/}{Stamford University  Bangladesh}, Bangladesh  \\ 
\textbf{Thesis on:}  Algorithm: Succinct Data Structure \\
\textbf{Interesting Courses:} Algorithms, Artificial Intelligence, Programming Language, OS, Compilers etc
CGPA: 3.73 (out of 4.00) \\
\textbf{Passing Year:} 2016

\vspace{10pt}  
 

  
 
\pagebreak
\section{\centerline{RECENT COMPLETED PROJECTS }}
\vspace{12pt} % Gap between title and text

 
\begin{enumerate}

  \item \textbf{Project :} Onest CRM Application [Customer Relationship Management]\\
 \textbf{Demo Link :}\href{https://crmv1.onestweb.com/}{ crmv1.onestweb.com}\\ 
 \small{Note: Onest CRM system is a powerful tool for managing customer relationships. Key features of a CRM system include centralizing customer data, improving communication, enhancing customer experience, increasing sales. By utilizing a CRM system, businesses can build stronger relationships with their customers, improve customer satisfaction, and drive growth.} \\
 \textbf{Tools:} HTML5, CSS, Bootstrap 5, JavaScript, jQuery, MySQL 8.0, PHP 8.1, Laravel 9.0 etc.\\
\textbf{Completed Date: } February 2023
\vspace{12pt}  


  \item \textbf{Project :} Land Loard Application [Property Rent and Buy Management]\\
 \textbf{Demo Link :}\href{https://landlord.onestweb.com/}{ landlord.onestweb.com}\\
 \small{Note: Onest LandLord software helps property managers, landlords, and real estate agents manage their rental and sales properties. It offers features such as property listings, tenant and buyer management, online payment processing, maintenance management, reporting and analytics, document management, communication and notifications.}\\
 \textbf{Tools:} HTML5, CSS, Bootstrap 5, JavaScript, jQuery, MySQL 8.0, PHP 8.1, Laravel 9.0 etc.\\
\textbf{Completed Date: } November 2022
\vspace{12pt}  

  \item \textbf{Project :} Onest HRM Software [Human Resource Management]\\
 \textbf{Demo Link :}\href{https://hrm.onesttech.com/}{ hrm.onesttech.com}\\ 
 \small{Note: Onest Human Resource Management (HRM) software is a tool that helps businesses manage their human resources functions. It offers features such as employee management, payroll and benefits administration, time and attendance tracking, performance management, recruitment and onboarding, training and development, and compliance and legal requirements.} \\
 \textbf{Tools:} HTML5, CSS, Bootstrap 5, JavaScript, jQuery, MySQL 8.0, PHP 8.1, Laravel 9.0 etc.\\
\textbf{Completed Date: } June 2022
\vspace{12pt}  



 \item \textbf{Project :} SOOKH [Ecommerce with ERP System]\\
 \textbf{Demo Link :}\href{https://sookh.com}{ www.sookh.com}\\ 
 \textbf{Note:} 
 \small{SOOKH is a Bangladeshi company specializing in online retailers and  online business on ecommerce platform. It is complete solution for e-commerce business.} \\
 \textbf{Using Languages:} HTML, CSS, Bootstrap, JavaScript, jQuery, Ajax, MySQL, PHP, Laravel etc.\\
\textbf{Completed Date: } 30 June 2021
\vspace{12pt}  


 \item \textbf{Project :} MyFragranceMe [Ecommerce with ERP]\\
 \textbf{Demo Link :}\href{http://demo.ahpretailoperation.com/testing/new/login}{ www.myfragranceme.com}\\ 
 \textbf{Note:} MyFragranceMe is a Dubai company specializing in online retailers and  online business on ecommerce platform. \\
 \textbf{Using Languages:} HTML, CSS, Bootstrap, JavaScript, jQuery, Ajax, MySQL, PHP, Laravel etc.\\
\textbf{Completed Date: } 06 January 2021
\vspace{12pt}  




 \item \textbf{Project :} InfixHub - Ultimate Digital Marketplace\\
 \textbf{Demo Link :}\href{http://infixhub.infixdev.com}{ www.infixhub.infixdev.com}\\
 \textbf{Codecanyon Link :}\href{https://codecanyon.net/item/infixhub-ultimate-digital-marketplace/29695967}{https://codecanyon.net/item/infixhub-ultimate-digital-marketplace/29695967}\\
 \textbf{Note:} In InfixHub Script, you can sell your projects without re-sellers, just need to install the script and add your products. Or you can set up your marketplace and accept any user to upload their products and get the selling commission.
It is developed by PHP and Laravel framework. \\
\textbf{Completed Date: } 16 December 2020
\vspace{12pt}  



 \item \textbf{Project :} InfixLMS - Open Source Learning Management System\\
 \textbf{Demo Link :}\href{http://lms.infixdev.com}{http://lms.infixdev.com}\\ 
 \textbf{Note:} In The most powerful online learning platform for all kinds of instructors.
Be a global teacher. Learn from anywhere, anytime. It is developed by PHP and Laravel framework. \\
\textbf{Completed Date: } 14 May 2019
\vspace{12pt}  

 

 \item \textbf{Project :} InfixBiz - Open Source Business Management ERP\\
 \textbf{Demo Link :}\href{https://business.infixlive.com}{https://business.infixlive.com}\\
 \textbf{Codecanyon Link :}\href{https://codecanyon.net/item/infix-business-management-erp/25350109}{https://codecanyon.net/item/infix-business-management-erp/25350109}\\
 \textbf{Note:} ERP is a Modern and responsive small Business management system. 
It is developed by PHP and Laravel framework. 
It is designed and develops for thinking shop, small business, company and any types of business. 
Here has accounting, management, invoice,user and data analysis.\\
\textbf{Completed Date: } 31 December 2019
\vspace{12pt}  



 \item \textbf{Project :} InfixEdu School - School Management System Software\\
 \textbf{Demo Link :}\href{http://demo.infixdev.com}{http://demo.infixdev.com}\\
 \textbf{Codecanyon Link :}\href{https://codecanyon.net/item/infix-school-academic-management-system/23876323}{https://codecanyon.net/item/infix-school-academic-management-system/23876323}\\
 \textbf{Note:} We have created INFIX in School Management ERP System which is extremely reliable, intuitive, and easy to use. It can cater to all your needs of managing school, college, university, and any other educational institution eliminating the tedious manual processes.
It is developed by PHP and Laravel framework. \\
\textbf{Completed Date: } 28 May 2019
\vspace{12pt}  

 
\end{enumerate}



\vspace{0.5in} 
\section{\centerline{OTHER ACTIVITIES}}

\vspace{0.2in}

\begin{enumerate}
\item I love teaching and I was an IT Instructor of C/C++ Programming Languages at  \textbf{Toha It Training Center} in 2015-2016
\item Trainer of \textbf{ACM Programming} of  Programming Group  of   \textbf{Stamford University Bangladesh}
\item Participate of several University  \textbf{ ACM Programming and App Contest}  such as EWU, BUBT, Daffodil, IUB, Stamford University etc. 
\item Runner's Up of  \textbf{University App Contest 2015} at Stamford University Bangladesh
  
 \item Participate of \textbf{NASA APP CHALLENGE 2016} at Independent University Bangladesh
\item Web design and developing as Freelancer 

\end{enumerate}
 
 
\section{\centerline{ INTEREST}}
\vspace{0.2in}

\begin{enumerate}
\item Research, Analysis and Programming etc.
\item Learn new Programming Language and make a project on it. 
\item Participate Code Challenge, Programming and App Contest etc.
\end{enumerate}

\vspace{.2in}
\pagebreak  

  



\end{resume}
\end{document}
